Singapore's Public Housing Affordability

### 2023-11-14 datastory.qmd
Project Update

<p style="text-align: justify;">
The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
</p>

![](docs/images/dreamhome.png){fig-align="center" width="698"}

@@

@@

<p style="text-align: justify;">
Hint: Pay attention to how 3-room flats almost hitting $1,000,000! On top of that, we can also visually compare the number of outliers in 1990 and 2022, denoted by the green and orange box respectively. 
</p>

@@

```{r, eval=FALSE,echo=FALSE}

@@

@@

### References
```{r}

>>>>

<p style="text-align: justify;">
The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
</p>
![](docs/images/dreamhome.png){fig-align="center" width="698"}

@@

```
<p style="text-align: justify;">
The interactive graph above compares 
</p>

@@

<p style="text-align: justify;">
Hint: Pay attention to how 3-room flats almost hitting \$1,000,000! On top of that, we can also visually compare the number of outliers in 1990 and 2022, denoted by the green and orange box respectively.
</p>

@@

<p style="text-align: justify;">
So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable for Singaporeans - compared with the average income earned.
</p>
```{r, eval=FALSE,echo=FALSE}

@@

<p style="text-align: justify;">
You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right! But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
</p>

<p style="text-align: justify;">

@@

### References

```{r}
